Scaling up the hyperparameter grid for Naomi

### 2023-06-12 src/dev_scale-grid/scale-grid.Rmd
Add marginal SD plot output to dev_scale-grid and rerun #49

```{r}
testrun <- parallel::mcparallel({TMB::sdreport(obj = fit$obj, par.fixed = fit$par, getJointPrecision = TRUE)})
sd_out <- parallel::mccollect(testrun, wait = TRUE, timeout = 0, intermediate = FALSE)
```

@@

```{r sd, class.source = 'fold-hide', fig.cap="Marginal standard deviations."}
sd <- sqrt(diag(sd_out$cov.fixed))

data.frame(par = names(sd), sd = unname(sd)) %>%
  ggplot(aes(x = reorder(par, sd), y = sd)) +
    geom_point(alpha = 0.6) +
    coord_flip() +
    lims(y = c(0, 2)) +
    theme_minimal() +
    labs(x = "", y = "SD from TMB")
```

@@

ggsave("tv-plot.png", plot = tv_plot, h = 4, w = 6.25)
```

@@

ggsave("reduced-rank-plot.png", reduced_rank_plot, h = 4, w = 6.25)
```

>>>>

```{r}
testrun <- parallel::mcparallel({TMB::sdreport(obj = fit$obj, par.fixed = fit$par, getJointPrecision = TRUE)})
sd_out <- parallel::mccollect(testrun, wait = TRUE, timeout = 0, intermediate = FALSE)
sd_out <- sd_out[[1]]
```

@@

```{r sd, class.source = 'fold-hide', fig.cap="Marginal standard deviations."}
cbpalette <- c("#56B4E9","#009E73", "#E69F00", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")

sd <- sqrt(diag(sd_out$cov.fixed))

(marginal_sd_plot <- data.frame(par = names(sd), sd = unname(sd)) %>%
  mutate(
    start = str_extract(par, "^[^_]+"),
    scale = fct_recode(start, "Log" = "log", "Logit" = "logit", "Other" = "OmegaT")
  ) %>%
  ggplot(aes(x = reorder(par, sd), y = sd, col = scale)) +
    geom_point(size = 2) +
    coord_flip() +
    scale_color_manual(values = c("#56B4E9","#009E73", "#E69F00")) +
    lims(y = c(0, 2)) +
    theme_minimal() +
    labs(x = "", y = "Marginal standard deviation", col = "Scale"))

ggsave("marginal-sd.png", plot = marginal_sd_plot, height = 3.5, w = 6.25)
```

@@

ggsave("tv-plot.png", plot = tv_plot, h = 3, w = 6.25)
```

@@

ggsave("reduced-rank-plot.png", reduced_rank_plot, h = 3.5, w = 6.25)
```
